Categorical and gradient aspects of wordlikeness\thanks{Thanks to Gene Buckley, Charles Yang, and audiences at NELS 43 for helpful comments.}

### 2012-11-11 1.tex
Completed writing on 2-4!

@@

>>>>

\section{A program for phonotactic theory}

Theories of phonotactic knowledge should be evaluated by the same stringentcriteria applied to other formal arenas: neither overgeneration nor undergeneration should be permitted. It will be shown that the orthodoxy that phonotactic knowledge is in some sense ``probabilistic'' suffers from quite severe over- and undergeneration.

This heuristic has the greatest impact regarding debates about ``abstractness'' of underlying representations. 
It cannot be said, precisely, that it either excludes or requires any particular type of abstractness.

Proposed restrictions on UR abstractness have been faulted for a number of reasons. In some cases, they preclude otherwise-desirable analyses of alternations. Another objection that could reasonably made is that any restriction on abstract URs that introduces an assymetry in URs is bad.
\citep[~chap.~1]{KK77}

@@

\citet{Shibatani1973}, however, argues that morpheme structure constraints cannot account for all wordlikeness constraints.
In German, for instance, final obstruents devoice, and as a result, there a
re pairs such  [ɡʀaːt]-[ɡʀaːtə] `ridge(s)' and [ɡʀaːt]-[ɡʀaːdə] `degree(s)'
 differing only in the plural shape of the root.
Since the voicing of final obstruents is contrastive, the restriction on th
e voicing of obstruents cannot be a morpheme structure constraint. 
Yet, \citeauthor{Shibatani1973} claims that native speakers reject nonce wo
rds ending in final voiced obstruents ``\emph{on the ground that they end i
n voiced obstruents}'' (95). 
Thus, not all constrasts in possible wordhood can be stated as morpheme str
ucture constraints.

Whereas \citeauthor{Shibatani1973} maintains that morpheme structure constraints are insufficient to account for speakers' knowledge of possible wordhood, others argue that morpheme structure constraints are also unnecessary. \citet[297]{Hale1965}, \citet{Kisseberth1970b}, and \citet[212f.]{Postal1968} observe that the structural descriptions of phonological processes often are often reflected in the lexical redundancies in the same language. In Russian, there are alternations implicating a process of obstruent voice assimilation, and tautomorphemic obstruent clusters have uniform voicing \citep[283]{A74}. \citet[205f.]{Dell1973} and \citet[28f.]{Stampe1973} argue that morpheme structure constraints are otiose, as phonological rules triggering alternations impose restrictions on the contents of URs, an effect known as \emph{Stampean occultation}.

Since at least \citet{Pike1947b}, linguists have posited language-specific constraints on the contents of underlying representations.
These \emph{morpheme structure constraints} were at one time thought to fully account for speakers' knowledge of possible and impossible words (e.g., \citealt{Chomsky1965}, \citeyear[382]{SPE}, \citealt[22f.]{SPR}, \citeyear{
Halle1962}, \citealt{Stanley1967}).
